Galois Characterization of Function Fields of \\ Transcendence Degree $1$ over Number Fields

### 2017-01-28 Master Thesis/introduction.tex
Add more notation

$\begin{array}{ll}
\mathbb{N} & \text{natural numbers} \\
\mathbb{Z} & \text{integers}\\
\mathbb{Q} & \text{rational numbers}\\
\mathbb{R} & \text{real numbers}\\
\mathbb{C} & \text{complex numbers}\\
\mathbb{Z}_p & \text{$p$-adic integers}\\
\mathbb{Q}_p & \text{$p$-adic numbers}\\
\\
\overline{K} & \text{algebraic closure of $K$}\\
K^\text{s} & \text{separable closure of $K$}\\
G_K & \text{absolute Galois group of $K$}
\end{array}$

>>>>

$\begin{array}{ll}
\mathbb{N} & \text{natural numbers} \\
\mathbb{Z} & \text{integers}\\
\mathbb{Q} & \text{rational numbers}\\
\mathbb{R} & \text{real numbers}\\
\mathbb{C} & \text{complex numbers}\\
\\
\overline{K} & \text{algebraic closure of $K$}\\
K^\text{s} & \text{separable closure of $K$}\\
K^\text{t} & \text{absolute inertia field of $K$}\\
K_v & \text{henselization of $K$ with respect to $v$}\\
G_K & \text{absolute Galois group of $K$}\\
\operatorname{Gal}(L/K) & \text{Galois group of $L/K$}\\
\operatorname{char}(K) & \text{characteristic of $K$}\\
\operatorname{trdeg}(L/K) & \text{transcendence degree of $L/K$}
\end{array}$
